\chapter{Introduction}

\section{Motivation}
Passenger comfort is a differentiating factor in premium aircraft cabins, especially in the VIP segment where the interior is expected to support work, rest, and quiet conversation. In this context, cabin noise is not only an engineering nuisance but also a design constraint that influences perceived quality, fatigue, and overall product value. The InnovAero task therefore requires a solution that is technically credible, compact, and compatible with aviation integration constraints.

\section{Report Purpose}
This report is structured to support a professional competition submission for Lufthansa Technik. It first defines the task and the relevant constraints, then reviews the literature, and finally derives a concept and a validation approach. The goal is not to present a finished certification package, but to establish a clear engineering argument that can be extended with calculations, simulations, and prototype data.

\section{Document Structure}
The following chapters provide a logical flow from context to solution.
\begin{itemize}
    \item Chapter 2 summarizes the competition task and the engineering requirements.
    \item Chapter 3 reviews the most relevant literature on cabin noise control.
    \item Chapter 4 proposes a system-level concept for the VIP cabin use case.
    \item Chapter 5 outlines a methodology for analysis, simulation, and evaluation.
    \item Chapter 6 concludes the report and identifies the next development steps.
\end{itemize}
