\chapter{Task Definition and Requirements}

\section{Competition Task}
The underlying task is to improve acoustic comfort in a VIP aircraft cabin using methods that are suitable for an engineering proposal delivered to Lufthansa Technik. The problem is inherently multidisciplinary because it combines acoustics, signal processing, structural integration, usability, and maintainability. A strong concept must therefore be evaluated not only by theoretical cancellation performance, but also by its feasibility as an aircraft interior solution.

\section{Key Requirements}
From an aerospace systems perspective, the most important requirements are low mass, low integration complexity, limited maintenance burden, robust operation under cabin variability, and a clear safety boundary around the active control functions. For a premium cabin, the design must also preserve the visual and spatial quality of the interior.

\section{Engineering Constraints}
The most relevant constraints are summarized below.
\begin{enumerate}
    \item The solution should target the dominant low-frequency noise components where active methods are most effective.
    \item The concept should remain localized enough to be installed around a seat group or premium zone rather than requiring full-cabin retrofit.
    \item The architecture should tolerate model mismatch and operational variation, especially in the secondary path.
    \item The design should allow passive trim to carry part of the load so that the active layer can remain compact.
    \item The evaluation method should include both physical performance and passenger-facing acoustic quality.
\end{enumerate}

\section{Success Criteria}
A successful submission should show that the chosen concept reduces the perceptually relevant noise components, can be integrated into a realistic cabin architecture, and is defensible against a review by aviation engineers. In practice, this means the report should explicitly connect the literature, the selected control strategy, and the expected implementation path.
